HealpixNet: Efficient spherical Convolutional Neural Networks with Healpix sampling for cosmological applications

### 2018-06-20 scnn.tex
going further

We compare the performance of the spherical CNN to two simple benchmark algorithms.
The two baselines are based on building features with a) the Power Spectral Densities or b) the histogram of pixels in the maps.
Those features are then classified use a Support Vector Machine (SVM) with a linear kernel. Other kernels did provide better result while having worse scaling properties.
For fairness, we augmented the dataset of the baseline in a similar way as for the network, i.e:

The histogram features contains information about the distribution of pixels, but does not include any spatial information.
Both the PSD features and the CNN can exploit the spatial information.

For The maps
The performance is assessed by measuring the classification error on a test set.

We compare the spherical CNN with a handcrafted feature classifier. CITE \cite{...}
The features are
constructed using a normalized histogram of the values. We then train a linear
SVN classifier. We tried different kernels, but they were not leading to better
results. For a fair comparison, we increase the amount of training data of the
SVN classifier until the testing error plateau to a fix value.

@@

>>>>

We compare the performance of the spherical CNN to two simple benchmark
algorithms. The two baselines are based on building features with a) the Power
Spectral Densities or b) the histogram of pixels in the maps. CITE~\cite{...}
After a normalization, those features are then classified use a Support Vector
Machine (SVM) with a linear kernel. Other kernels did provide better result
while having worse scaling properties. For fairness, we augmented the dataset
of the baseline algorithm in a similar way as for the network, i.e, with
created an "unlimited" number of samples by adding new random realizations of
the noise. We stop adding new samples in the classifier once the validation
error converge to a values. This process is depicted in
Figure~\ref{fig:hist_error_evolution}.

The maps are separated into a training and a testing set. The performance is
assessed by measuring the classification error on a test set. Once the
training maps are sliced into samples, we split them into a training samples
and validation samples. The validation samples is used to tune the
regularization parameter of the SVM using a standard cross-validation
technique\footnote{We also give a small advantage to the SVM classifiers by
using cross-validation on the testing set.}.

@@

The histogram features contains information about the distribution of pixels, but does not include any spatial information.
In contrast, both the PSD features and the CNN can exploit the spatial information.
